Amazonian Narratives in Presidential Discourse (1985 to 2020)

### 2021-11-08 08112021_Sposito---Silva_Muller_DRAFT.Rmd
#text in #added stop words # changed freq table to plot

# Visualize correlations
am_narratives <- Amazon_speeches %>%
  select(-c(context, text, fulltext, president, party, date, title, doc_id, location)) %>%
  tidyr::pivot_longer(sovereignty:other) %>% 
  group_by(year, name) %>% 
  summarise(value = sum(value)) %>% 
  rename(narrative = name)
ggplot(am_narratives, aes(x = year, y = value , fill = narrative)) +
  geom_line(aes(group = narrative, color = narrative), size = 1) +
  labs(x = "Year",
       y = "",
       title = "Narratives in Presidential Speeches per year since 1985 in Brazil")+
    facet_wrap(~narrative)

# Same frequency table but normalized by the numbers of speeches in broader dataset
pres_narratives_n <- pres_narratives %>%
  mutate(n_speeches = summary(as.factor(BR_Presidential_Speeches$president))) %>%
  mutate(across(c(2:6), .fns = ~./n_speeches)) %>%
  select(-n_speeches) %>%
  mutate_if(is.numeric, round, digits = 2)
kableExtra::kbl(pres_narratives_n, caption = "Narratives per President in Brazil (normalized)") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")

# Table by stage
stage_narratives <- Amazon_speeches %>%
  mutate(stage = Amazon_lc$stage) %>%
  select(-c(context, text, fulltext, year, party, date, title, doc_id, location, president)) %>%
  group_by(stage) %>%
  summarise(across(everything(), sum))
kableExtra::kbl(stage_narratives, caption = "Narratives per President in Brazil") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")

# Table by stage, normalized
stage_narratives_n <- stage_narratives %>%
  mutate(n_stages = summary(as.factor(Amazon_lc$stage))) %>%
  mutate(across(c(2:6), .fns = ~./n_stages)) %>%
  select(-n_stages) %>%
  mutate_if(is.numeric, round, digits = 2)
kableExtra::kbl(stage_narratives_n, caption = "Narratives per President in Brazil (normalized)") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
```

>>>>

# Visualize correlations
am_narratives <- Amazon_speeches %>%
  dplyr::select(-c(context, text, fulltext, president, party, date, title, doc_id, location)) %>%
  tidyr::pivot_longer(sovereignty:other) %>% 
  group_by(year, name) %>% 
  summarise(value = sum(value)) %>% 
  rename(narrative = name)

ggplot(am_narratives, aes(x = year, y = value , fill = narrative)) +
  geom_line(aes(group = narrative, color = narrative), size = 1) +
  labs(x = "Year",
       y = "",
       title = "Narratives in Presidential Speeches per year since 1985 in Brazil")+
    facet_wrap(~narrative)

# Same frequency table but normalized by the numbers of speeches in broader dataset
pres_narratives <- Amazon_speeches %>%
  select(-c(context, text, fulltext, year, party, date, title, doc_id, location)) %>%
  group_by(president) %>%
  summarise(across(everything(), sum))

pres_narratives_n <- pres_narratives %>%
  mutate(n_speeches = summary(as.factor(BR_Presidential_Speeches$president))) %>%
  mutate(across(c(2:6), .fns = ~./n_speeches)) %>%
  select(-n_speeches) %>%
  mutate_if(is.numeric, round, digits = 2)
kableExtra::kbl(pres_narratives_n, caption = "Narratives per President in Brazil (normalized)") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")

# Table by stage, normalized
stage_narratives <- Amazon_speeches %>%
  mutate(stage = Amazon_lc$stage) %>%
  select(-c(context, text, fulltext, year, party, date, title, doc_id, location, president)) %>%
  group_by(stage) %>%
  summarise(across(everything(), sum))

stage_narratives_n <- stage_narratives %>%
  mutate(n_stages = summary(as.factor(Amazon_lc$stage))) %>%
  mutate(across(c(2:6), .fns = ~./n_stages)) %>%
  select(-n_stages) %>%
  mutate_if(is.numeric, round, digits = 2)
kableExtra::kbl(stage_narratives_n, caption = "Narratives per President in Brazil (normalized)") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Times New Roman")
```
